---
title: "R Markdown & Plotly"
author: "GuiLopes"
date: "7/10/2020"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## mtcars: code
I work for a car company.

The execs recently asked the data science team to find a way to increase mileage per gallon of their cars.

Analysis of data from a random sample of cars revealed an association between mileage per gallon and car weight.

This is the code we used:

```{r, eval = FALSE, echo = TRUE, warning = FALSE}
suppressPackageStartupMessages(library(plotly))

plot_ly(mtcars, 
        x = mtcars$wt, 
        y = mtcars$mpg, 
        type = "scatter", 
        mode = "markers")
```

## mtcars: Plotly plot
The plot below is the output of the code:

```{r, echo = FALSE, warning = FALSE}
suppressPackageStartupMessages(library(plotly))
plot_ly(mtcars, x = mtcars$mpg, y = mtcars$wt, type = "scatter", mode = "markers")
```

## mtcars: results
As you can see, it *appears* that the lighter the car the more miles per gallon. 
However, the execs were not convinced that a solution would be to invest in car weight technology.

We then estimated the probability of finding this association (p-value) if there was 
no association between car weight and mileage per gallon (null hypothesis)?

```{r, echo = TRUE}
mpgwt <- lm(mtcars$mpg ~ mtcars$wt)
summary(mpgwt)$coefficients[2,4] %>% format(scientific = FALSE)
```

The probability is less than 0.05. The execs were convinced.

## mtcars: assignment

Thank you!
