---
title: "Coursera: Developing Data Products // R Markdown and Leaflet Assignment"
author: "Gui Lopes"
date: "7/10/2020 10:58AM"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Welcome to the folklore of Lencois Maranhenses

The region marked in the map is called "Lencois Maranhenses".

Legend says a Dutch battle ship intercepted a piracy attempt in the Atlantic 
Ocean, but the pirates managed to escape by suddenly diverging their route to a 
location that at the time was unknown to Europeans (the "Lencois Maranhenses").

The pirates buried the treasure in the dunes, but their ship sunk on their way 
back to the Caribbeans along with all records of the treasure's location.

One pirate stayed in-land after falling in love with a native. The only hint
he shared was that the treasure is near a bank of green water.

Is this true? No one really knows. If found, this treasure would have an 
immeasurable value from an archaeological point of view.

The movie "The House of Sand" was filmed in this region, in case you're curious.

https://en.wikipedia.org/wiki/The_House_of_Sand

This mind blowing place also happens to be near my hometown.

```{r}
library(leaflet)
map <- leaflet() %>% 
  addTiles() %>%
  addMarkers(lat = -2.4859, lng = -43.1284, popup = "Lencois Maranhenses")
map
```